---
title: "linear model from Web"
author: "Keren Gonzalez"
date: "Fall 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
plot(SIMS~ARM,data=data)
```

The scatterplot seems to show the plot is moving upward to the right. I suspect that there is a positive correlation due to the data going uphill to the right.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation we have found is 0.69, which is a positive correlation.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation of a line is y=mx+b. 
The fit equation is SIMS= 0.054563*ARM-4.095160

#### Predict at target point

SIMS= 0.054563*88-4.095160
```{r}
0.054563*88-4.095160
```

When we plugged in 88 for ARM in our best fit equation, we got 0.706, and that will be our prediction.

```{r}
new <- data.frame(ARM = 88, GRIP=94)
```

```{r}
predict(model.1, new, INTERVAL = "prediction")
```


Using the predict function also gives us the same result, 0.706384.

#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
basicNN + geom_point() + geom_smooth(method=lm)
```

Here is the best fit line for our data, and we can see that if we look for an x-value of 88 for arm, the y-value is about 0.7 as predicted.

## Model 2 SIM~GRIP



### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

This scatterplot shows a positive correlation since the points increase to the right.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

GRIP has a smaller correlation with SIMS with GRIP versus SIMS with ARM. 

### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

If we look at the adjusted R-squared value of this GRIP data, it is smaller than the ARM data's adjusted R-square. In addition, the residual standard error is larger for this GRIP data than the ARM data. Both of these values indicate that Model 1 is doing a better job at explaining our prediction, and a better model.

#### predict model.2 at target point

```{r}
predict(model.2, new, interval = "prediction")
```
```{r}
0.045463*94-4.809675
```

Our prediction value is -0.5361543.

#### now add the model fit to our plot for model.2
  
```{r}
basicNN <- ggplot(data, aes(y=SIMS, x=GRIP))
basicNN + geom_point() + geom_smooth(method = lm)
```


Here is the result of the scatter plot and our best fit line for our GRIP and SIMS data. If we use our prediction value it matches x=94 for GRIP.


## Model 3 SIM~ARM+GRIP



### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

We have a positive correlation between both arm and grip data. This number, 0.7326545, is higher than the correlation of just ARM and SIMS(0.6860073) or GRIP and SIMS(0.63980073).

### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM + GRIP,data=data)
summary.lm(model.3)
```

SIMS = -5.433871 + GRIP * 0.024470 + ARM * 0.037311 is the equation. The adjusted R-squared is 0.5358 which is bigger and the residual error is smaller and this indicates this as a superior model compared to the previous ones.


#### predict model.3 at target point
  
```{r}
predict(model.3, new, interval = "prediction")
```



## Comparing nested models ANOVA Test

### Model.1 vs Model.3
```{r}
anova(model.1,model.3)
```
Model 2 is actually model 3, and when we add up all of the errors in this model we have 29.45 errors versus model1. This means that GRIP and ARM in a model is better than just ARM.


### Model.2 vs Model.3

```{r}
anova(model.2,model.3)
```

This one went from 243.07 to 188.43 and this is also a significant change as we can see from the even smaller Pr(>F). This indicates model 3 is better versus model 2 that just used GRIP.

## Informally compare Model.1 with model.2

```{r}
anova(model.1, model.2)
```
Model 1 has a smaller RSS of 217.88 vs 243.07(model 2). Informally, model 1 is better using SIMS ~ ARM is a better model.

